---
title: "Data Manipulation"
output: html_notebook
---

```{r,echo=FALSE}
library(dplyr,warn.conflicts = FALSE)
library(lubridate,warn.conflicts = FALSE)
```

```{r,echo=FALSE}
languages <- c('c','chash','cplus','java','javascript','php','python')

loc <- paste('C:/Users/mmore/Dropbox/Econometrics II - TA/Project/GitHub/Data/commits/',
             languages[1],
             '_commits_202003.csv',
             sep='')

df_commits <- read.csv(loc)
df_commits$language <- 'c'   
df_commits$language_code <- 1 

i <- 2
for (language in languages[-1]){
  
  loc <- paste('C:/Users/mmore/Dropbox/Econometrics II - TA/Project/GitHub/Data/commits/',
               language,
               '_commits_202003.csv',sep='')
  df_temp <- read.csv(loc)
  df_temp$language <- language 
  df_temp$language_code <- i 

  df_commits <- rbind(df_commits,df_temp)
  
  i <- i + 1

}

rm(df_temp)
```

```{r,echo=FALSE}
head(df_commits)
colnames(df_commits)[colnames(df_commits) == 'id'] <- 'commit_id'
colnames(df_commits)[colnames(df_commits) == 'commit_created_at'] <- 'commit_time'
df_commits$commit_time <- as.Date(sub(" .*","",as.character(df_commits$commit_time)),
                                  format='%Y-%m-%d')
```

```{r}
n_projects <- length(unique(df_commits$project_id))
n_committers <- length(unique(df_commits$author_id))
```

There are a total of `r n_projects` projects, and `r n_committers` users have contributed to such projects. 

# Users 

```{r,echo=FALSE}

commits_author <- df_commits %>% 
                  count(project_id,author_id) %>%
                  group_by(author_id) %>% 
                  summarise(total = sum(n))

quants <- quantile(commits_author$total,probs = c(0.80,0.90,0.95,0.99))

var_80 <- round(sum(filter(commits_author,total > quants[1])$total)/sum(commits_author$total) * 100,1)
var_90 <- round(sum(filter(commits_author,total > quants[2])$total)/sum(commits_author$total) * 100,1)
var_95 <- round(sum(filter(commits_author,total > quants[3])$total)/sum(commits_author$total) * 100,1)
var_99 <- round(sum(filter(commits_author,total > quants[4])$total)/sum(commits_author$total) * 100,1)


```

We define productivity of a user as the total number of commits that a person has made since they joined Github. Here we focus on the subsample of users who have made at least one commit. 

* The top 20% most productive users (i.e. with at least `r quants[1]` commits) contribute to nearly `r var_80`% of the total commits.

* The top 10% most productive users (i.e. with at least `r quants[2]` commits) contribute to nearly `r var_90`% of the total commits.

* The top 5% most productive users (i.e. with at least `r quants[3]` commits) contribute to nearly `r var_95`% of the total commits.

* The top 1% most productive users (i.e. with at least `r quants[4]` commits) contribute to nearly `r var_99`% of the total commits.

# Projects
```{r}
commits_project <- df_commits %>% 
                   group_by(project_id) %>% 
                   summarise(total_commits = n()) 

var_10 <- round(ecdf(commits_project$total_commits)(10) * 100, 1)
var_100 <- 100 - round(ecdf(commits_project$total_commits)(100) * 100, 1)
```

* `r var_10`% of the projects have at most 10 commits.  
* `r var_100`% of the projects have at least 100 commits.  

Is it true that more productive users, i.e. users that have a higher number of commits, are also involved in more projects? 

```{r}
df <- df_commits %>% 
        group_by(author_id) %>% 
        summarise(total_commit = n(), n_projects = n_distinct(project_id)) 

thresholds <- c(0,25,50,75,100,250,500,20000)
store <- matrix(0,2,length(thresholds)-1)

for (i in 1:(length(thresholds)-1)){
  store[,i] <- as.numeric(filter(df,total_commit >=thresholds[i] & total_commit < thresholds[i+1])
                          %>% summarise(mean(n_projects),n()))
}

colnames(store) <- c('<25','[25,50)','[50,75)','[75,100)','[100,250)','[250,500)','500+')
rownames(store) <- c('Avg. Number of Project','N. Authors')
write.csv(store,'C:/Users/mmore/Dropbox/Econometrics II - TA/Project/GitHub/Output/table_1.csv')
View(store)
rm(df)
```

# Time Trends in Total Number of Commits

```{r,echo=FALSE}
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')

df <- df_commits %>% 
      group_by(month=floor_date(commit_time,"month")) %>%
      summarize(monthly_commits=n()) %>%
      filter(month>=start_date) %>%
      filter(month<=end_date)

plot(seq(start_date,end_date,by='month'),
     df$monthly_commits,
     xlab='Date',
     ylab='N. Commits',
     main='Total Number of Monthly Commits over Time')

rm(df)
```

```{r,echo=FALSE}
plot_commits <-function(lng){
  
  start_date <- as.Date('2009-06-01')
  end_date <- as.Date('2019-05-01')
  
  df <- df_commits %>% 
        filter(language==lng) %>%
        group_by(month=floor_date(commit_time,"month")) %>%
        summarize(monthly_commits=n()) %>%
        filter(month>=start_date) %>%
        filter(month<=end_date)

  plot(seq(start_date,end_date,by='month'),
       df$monthly_commits,
       xlab='Date',
       ylab='N. Commits',
       main=paste('Total Number of Monthly Commits over Time, ',as.character(lng),sep= ' '))
  
}

```

```{r}
plot_commits('C')  
plot_commits('python')
plot_commits('javascript')
plot_commits('php')
plot_commits('java')
plot_commits('chash')
```


# Time Trends in Number of Active Projects

```{r,echo=FALSE}
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')

df <- df_commits %>% 
      group_by(month=floor_date(commit_time,"month")) %>%
      summarize(n_active_projects=n_distinct(project_id)) %>%
      filter(month>=start_date) %>%
      filter(month<=end_date)

plot(seq(start_date,end_date,by='month'),
     df$n_active_projects,
     xlab='Date',
     ylab='N. Projects',
     main='Total Number of Active Projects over Time')

rm(df)
```




# Productive Users

Vasilescu uses as a way to measure *productive* users the following metrics:

1. at least 500 commits to at least 10 non-forked repositories
2. at least 5 years between their first and last commit

They identify approximately 1300 users that fall in the category of *productive* users. They solve the problem of aliases, i.e. users who that commit to projects under different names. Vasilescu through some heuristics estimates that approximately 30% of users have multiples alises. 


```{r,echo=FALSE}
period <- 'month'

#Exclude commits that have been made before 2010
df_commits <- df_commits %>% filter(commit_time>=as.Date('2010-01-01'))

#Create users level statistics
df_u <- df_commits %>% 
        group_by(author_id) %>%
        summarise(first_commit=min(floor_date(commit_time,period)),
                  last_commit=max(floor_date(commit_time,period)),
                  total_commits=n(),
                  n_projects=n_distinct(project_id),
                  n_languages=n_distinct(language_code)) %>%
                  mutate(time_active=last_commit-first_commit,
                  )

#Filter by productivity filter
n_year <- 1 * 365
projects <- 2
commits <- 50

df_u <- df_u %>% 
        filter(n_projects>= projects) %>%
        filter(total_commits >= commits) %>%
        filter(time_active >= n_year)    

#Create users-month level statistics
df_um <- df_commits %>% 
         group_by(author_id, period=floor_date(commit_time,period)) %>%
         summarize(period_commits=n(),
         period_project=n_distinct(project_id)) 

#Augment the users-month dataset with missing month (i.e. when user did not make any commit)
if (period=='week'){
  start_date <- as.Date('2010-01-03')
}
if (period=='month'){
  start_date <- as.Date('2010-01-03')
}
end_date <- as.Date('2019-05-01')

df_temp <- expand.grid(author_id = unique(df_u$author_id),
                       period = seq(start_date,end_date,by=period))

df_um <- df_temp %>%
         left_join(df_um, by = c("author_id",'period'))

df_um$period_commits[is.na(df_um$period_commits)] <- 0 
df_um$period_project[is.na(df_um$period_project)] <- 0 


#Join the two databses
df <- df_um %>%
      left_join(df_u,by='author_id')

#Filter based on activity measures
n_active_users <- length(unique(df$author_id))

loc <- paste('C:/Users/mmore/Dropbox/Econometrics II - TA/Project/GitHub/Data/commits/productive_users_50_2_',
             period,
             ',.csv')

write.csv(df,loc)

```

# Filter used to classify higly productive users

There are a total number of `r n_active_users` users who:

* are active for at least `r as.integer(n_year/365)` years
* have contributed to at least `r projects` projects
* have made at least `r commits` commits


# Variable Description

* *author_id*: user identifier
* *month*: period of reference
* *monthly_commits*: total number of commits made in a month
* *monthly_project*: number of different project a user commited in a month
* *first_commit*: month in which user made the first recorded commit
* *last_commit*: month in which user made the last recorded commit
* *total_commits*: total number of commits made by a user over time
* *number_project*: total number of projects an user made contribution to
* *time active*: number of days between first and last commit 
* *n_languages*: number of languages an author has committed in hist life
```{r}
h <- hist(df_u$n_languages, breaks = 100, plot=FALSE,title='N. Languages')
h$counts=h$counts/sum(h$counts)
plot(h)

```


