---
title: "Data Manipulation"
output:
  html_document:
    df_print: paged
---

```{r,echo=FALSE}
library(dplyr,warn.conflicts = FALSE)
library(lubridate,warn.conflicts = FALSE)
options(warnings = -1)
```

```{r,echo=FALSE}
languages <- c('c','chash','cplus','java','javascript','php','python')

loc <- paste('C:/Users/mmore/Dropbox/GitHub/Data/commits/',
             languages[1],
             '_commits_202003.csv',
             sep='')

df_commits <- read.csv(loc)
df_commits$language <- 'c'   
df_commits$language_code <- 1 

i <- 2
for (language in languages[-1]){
  
  loc <- paste('C:/Users/mmore/Dropbox/GitHub/Data/commits/',
               language,
               '_commits_202003.csv',sep='')
  df_temp <- read.csv(loc)
  df_temp$language <- language 
  df_temp$language_code <- i 

  df_commits <- rbind(df_commits,df_temp)
  
  i <- i + 1

}


head(df_commits)
colnames(df_commits)[colnames(df_commits) == 'id'] <- 'commit_id'
colnames(df_commits)[colnames(df_commits) == 'commit_created_at'] <- 'commit_time'
df_commits$commit_time <- as.Date(sub(" .*","",as.character(df_commits$commit_time)),
                                  format='%Y-%m-%d')
```

```{r}
n_projects <- length(unique(df_commits$project_id))
n_committers <- length(unique(df_commits$author_id))
```

There are a total of `r n_projects` projects, and `r n_committers` users have contributed to such projects. 

# Users 

```{r,echo=FALSE}

commits_author <- df_commits %>% 
                  count(project_id,author_id) %>%
                  group_by(author_id) %>% 
                  summarise(total = sum(n))

quants <- quantile(commits_author$total,probs = c(0.80,0.90,0.95,0.99))

var_80 <- round(sum(filter(commits_author,total > quants[1])$total)/sum(commits_author$total) * 100,1)
var_90 <- round(sum(filter(commits_author,total > quants[2])$total)/sum(commits_author$total) * 100,1)
var_95 <- round(sum(filter(commits_author,total > quants[3])$total)/sum(commits_author$total) * 100,1)
var_99 <- round(sum(filter(commits_author,total > quants[4])$total)/sum(commits_author$total) * 100,1)


```

We define productivity of a user as the total number of commits that a person has made since they joined Github. Here we focus on the subsample of users who have made at least one commit. 

* The top 20% most productive users (i.e. with at least `r quants[1]` commits) contribute to nearly `r var_80`% of the total commits.

* The top 10% most productive users (i.e. with at least `r quants[2]` commits) contribute to nearly `r var_90`% of the total commits.

* The top 5% most productive users (i.e. with at least `r quants[3]` commits) contribute to nearly `r var_95`% of the total commits.

* The top 1% most productive users (i.e. with at least `r quants[4]` commits) contribute to nearly `r var_99`% of the total commits.

# Projects
```{r}
commits_project <- df_commits %>% 
                   group_by(project_id) %>% 
                   summarise(total_commits = n()) 

var_10 <- round(ecdf(commits_project$total_commits)(10) * 100, 1)
var_100 <- 100 - round(ecdf(commits_project$total_commits)(100) * 100, 1)
```

* `r var_10`% of the projects have at most 10 commits.  
* `r var_100`% of the projects have at least 100 commits.  



Is it true that more productive users, i.e. users that have a higher number of commits, are also involved in more projects? 

```{r}
df <- df_commits %>% 
        group_by(author_id) %>% 
        summarise(total_commit = n(), n_projects = n_distinct(project_id)) 

thresholds <- c(0,25,50,75,100,250,500,20000)
store <- matrix(0,2,length(thresholds)-1)

for (i in 1:(length(thresholds)-1)){
  store[,i] <- as.numeric(filter(df,total_commit >=thresholds[i] & total_commit < thresholds[i+1])
                          %>% summarise(mean(n_projects),n()))
}

colnames(store) <- c('<25','[25,50)','[50,75)','[75,100)','[100,250)','[250,500)','500+')
rownames(store) <- c('Avg. Number of Project','N. Authors')
write.csv(store,'C:/Users/mmore/Dropbox/GitHub/Output/table_1.csv')
print(round(store,0))
rm(df)
```

# Time Trends in Total Number of Commits

```{r,echo=FALSE}
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')

df <- df_commits %>% 
      group_by(month=floor_date(commit_time,"month")) %>%
      summarize(monthly_commits=n()) %>%
      filter(month>=start_date) %>%
      filter(month<=end_date)

plot(seq(start_date,end_date,by='month'),
     df$monthly_commits,
     xlab='Date',
     ylab='N. Commits',
     main='Total Number of Monthly Commits over Time')

rm(df)
```

```{r,echo=FALSE}
plot_commits <-function(lng){
  
  start_date <- as.Date('2009-06-01')
  end_date <- as.Date('2019-05-01')
  
  df <- df_commits %>% 
        filter(language==lng) %>%
        group_by(month=floor_date(commit_time,"month")) %>%
        summarize(monthly_commits=n()) %>%
        filter(month>=start_date) %>%
        filter(month<=end_date)

  plot(seq(start_date,end_date,by='month'),
       df$monthly_commits,
       xlab='Date',
       ylab='N. Commits',
       main=paste('Total Number of Monthly Commits over Time, ',as.character(lng),sep= ' '))
  
}

```

```{r}
#plot_commits('C')  
#plot_commits('python')
#plot_commits('javascript')
#plot_commits('php')
#plot_commits('java')
#plot_commits('chash')
```


# Time Trends in Number of Active Projects

```{r,echo=FALSE}
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')

df <- df_commits %>% 
      group_by(month=floor_date(commit_time,"month")) %>%
      summarize(n_active_projects=n_distinct(project_id)) %>%
      filter(month>=start_date) %>%
      filter(month<=end_date)

plot(seq(start_date,end_date,by='month'),
     df$n_active_projects,
     xlab='Date',
     ylab='N. Projects',
     main='Total Number of Active Projects over Time')

rm(df)
```




# Productive Users

Vasilescu uses as a way to measure *productive* users the following metrics:

1. at least 500 commits to at least 10 non-forked repositories
2. at least 5 years between their first and last commit

They identify approximately 1300 users that fall in the category of *productive* users. They solve the problem of aliases, i.e. users who that commit to projects under different names. Vasilescu through some heuristics estimates that approximately 30% of users have multiples alises. 


```{r,echo=FALSE}
period <- 'month'

#Exclude commits that have been made before 2010
df_commits <- df_commits %>% filter(commit_time>=as.Date('2010-01-01'))

#Create users level statistics
df_u <- df_commits %>% 
        group_by(author_id) %>%
        summarise(first_commit=min(floor_date(commit_time,period)),
                  last_commit=max(floor_date(commit_time,period)),
                  total_commits=n(),
                  n_projects=n_distinct(project_id),
                  n_languages=n_distinct(language_code)) %>%
                  mutate(time_active=last_commit-first_commit,
                  )

#Filter by productivity filter
n_year <- 1 * 365
projects <- 2
commits <- 50

df_u <- df_u %>% 
        filter(n_projects>= projects) %>%
        filter(total_commits >= commits) %>%
        filter(time_active >= n_year)    

#Create users-month level statistics
df_um <- df_commits %>% 
         group_by(author_id, period=floor_date(commit_time,period)) %>%
         summarize(period_commits=n(),
         period_project=n_distinct(project_id)) 

#Augment the users-month dataset with missing month (i.e. when user did not make any commit)
if (period=='week'){
  start_date <- as.Date('2010-01-03')
}
if (period=='month'){
  start_date <- as.Date('2010-01-03')
}
end_date <- as.Date('2019-05-01')

df_temp <- expand.grid(author_id = unique(df_u$author_id),
                       period = seq(start_date,end_date,by=period))

df_um <- df_temp %>%
         left_join(df_um, by = c("author_id",'period'))

df_um$period_commits[is.na(df_um$period_commits)] <- 0 
df_um$period_project[is.na(df_um$period_project)] <- 0 


#Join the two databses
df <- df_um %>%
      left_join(df_u,by='author_id')

#Filter based on activity measures
n_active_users <- length(unique(df$author_id))

loc <- paste('C:/Users/mmore/Dropbox/GitHub/Data/commits/productive_users_50_2_',
             period,
             ',.csv')

write.csv(df,loc)

```

# Filter used to classify higly productive users

There are a total number of `r n_active_users` users who:

* are active for at least `r as.integer(n_year/365)` years
* have contributed to at least `r projects` projects
* have made at least `r commits` commits


# Variable Description

* *author_id*: user identifier
* *month*: period of reference
* *monthly_commits*: total number of commits made in a month
* *monthly_project*: number of different project a user commited in a month
* *first_commit*: month in which user made the first recorded commit
* *last_commit*: month in which user made the last recorded commit
* *total_commits*: total number of commits made by a user over time
* *number_project*: total number of projects an user made contribution to
* *time active*: number of days between first and last commit 
* *n_languages*: number of languages an author has committed in hist life

```{r}
h <- hist(df_u$n_languages, breaks = 100, plot=FALSE)
h$counts=h$counts/sum(h$counts)
plot(h,
     main='N. Languages',
     xlab='')

```


# Projects Life-Cycle


```{r,include=FALSE}
period <- 'month'
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')


df <- df_commits %>%
      group_by(month=as.Date(floor_date(commit_time,period)),project_id) %>%
      summarize(n_commits=n(),monthly_n_authors=n_distinct(author_id)) %>%
      filter(month>=start_date) %>%
      filter(month<=end_date)

df_p <- df_commits %>%
        group_by(project_id) %>%
        summarize(project_created_at=min(commit_time),
                  last_commit=max(commit_time),
                  total_commits=n(),
                  n_authors=n_distinct(author_id))

df_t <- expand.grid(project_id = unique(df$project_id),
                    month = seq(start_date,end_date,by=period))

df <- df_t %>%
      left_join(df,by=c('month','project_id'))

rm(df_t)

df$n_commits[is.na(df$n_commits)] <- 0 

df <- df %>% 
      left_join(df_p,by='project_id') %>%
      filter(project_created_at>=start_date) %>%
      filter(month>=project_created_at)

rm(df_p)

df$project_age <- year(df$month) * 12 + month(df$month) - 12 * year(df$project_created_at) - month(df$project_created_at)
df$months_active <- year(df$last_commit) * 12 + month(df$last_commit) - 12 * year(df$project_created_at) - month(df$project_created_at)


df$monthly_n_authors[is.na(df$monthly_n_authors)] <- 0
```

```{r,echo=FALSE}
df_temp <- df %>%
           group_by(project_id) %>%
           summarise(total_commits=max(total_commits),months_active=max(months_active),n_authors=max(n_authors))

store <- matrix(0,6,8)           

store_fun<- function(df_temp,lb,ub){
  
  return(as.numeric(df_temp %>% filter(months_active>=lb,months_active<=ub) %>% summarise(n_projects = n(),mean(total_commits),max(total_commits),median(total_commits),mean(n_authors),max(n_authors),median(n_authors))))

  }


store[1,1:7] <- store_fun(df_temp,0,1)
store[2,1:7] <- store_fun(df_temp,2,3)
store[3,1:7] <- store_fun(df_temp,4,6)
store[4,1:7] <- store_fun(df_temp,7,12)
store[5,1:7] <- store_fun(df_temp,13,36)
store[6,1:7] <- store_fun(df_temp,37,1000)
store[,8] <- store[,1]/ sum(store[,1])

colnames(store) <- c('N. Projects','Mean Total Commits','Max Total Commits','Median Total Commits','Mean N. Authors','Max N. Authors', 'Median N. Authors','Shere of Total Projects')
rownames(store) <- c('1 month','2-3 months', '4-6 months', '7-12 months', '13-36 months', '36+ months')
print(round(store,3))
```

#New Projects

```{r}

df_temp <- df %>%
           group_by(month) %>%
           filter(project_age==0) %>%
           summarise(n_new_projects=n()) %>%
           filter(month>=start_date,month<=end_date)


plot(df_temp$month,df_temp$n_new_projects,
     xlab='Time',
     ylab='Number',
     main='Number of New Projects over Time')


```



```{r}
new_plot <- function(df,lb,ub){
  
        df_temp <- df %>% 
                   group_by(project_id) %>% 
                   filter(sum(n_commits)>=lb,sum(n_commits)<=ub)
        
        print(length(unique(df_temp$project_id)))
        
        df_temp <- df_temp %>%
                   group_by(project_age) %>%
                   summarise(n=mean(n_commits),
                             p=mean(as.numeric(n_commits>0)),
                             p10=mean(as.numeric(n_commits>10)),
                             mean_authors=mean(monthly_n_authors))
        par(mfrow=c(2,2))

        plot(df_temp$n,
             xlab='Age of the Projects in Months',
             ylab='N. Commits',
             main='Monthly Commits vs. Age of Project')


        plot(df_temp$p[2:84],
             xlab='Age of the Projects in Months',
             ylab='Probability',
             main='Probability Project gets at 
                   least 1 commit vs. Age')

        plot(df_temp$p10[2:84],
             xlab='Age of the Projects in Months',
             ylab='Probability',
             main='Probability Project gets at 
                   least 10 commit vs. Age')
        
        plot(df_temp$mean_authors[2:84],
             xlab='Age of the Projects in Months',
             ylab='N. Authors',
             main='Average N. of Authors 
                   Per Month vs. Age')
        

 
        return()       
}

new_plot(df,1,500)

new_plot(df,501,2500)

new_plot(df,2501,100000)
```


#Users Life-Cycle

Here we want to investigate some statistics about the contribution history of users during their life on GitHub. 

```{r,echo=FALSE}
period <- 'month'
start_date <- as.Date('2009-06-01')
end_date <- as.Date('2019-05-01')

#Characteristic Author-Month

df_commits$commit_month <- as.Date(floor_date(df_commits$commit_time,period))
df_commits$date <- month(df_commits$commit_month) + year(df_commits$commit_month) * 12

df <- df_commits %>%
      group_by(month=as.Date(floor_date(commit_time,period)),author_id) %>%
      summarize(n_commits=n(),
                n_projects_monthly=n_distinct(project_id))

#Characteristic of the Author

df_p <- df_commits %>%
        group_by(author_id) %>%
        summarize(author_first_commit=min(commit_time),
                  n_projects=n_distinct(project_id),
                  author_last_commit=max(commit_time),
                  n_languages=n_distinct(language_code),
                  total_commits=n(),
                  n_active_months=n_distinct(date))

df_t <- expand.grid(author_id = unique(df$author_id),
                    month = seq(start_date,end_date,by=period))

df <- df_t %>%
      left_join(df,by=c('month','author_id'))

rm(df_t)

df$n_commits[is.na(df$n_commits)] <- 0 
df$n_projects_monthly[is.na(df$n_projects_monthly)] <- 0 

df <- df %>% 
      left_join(df_p,by="author_id") 

rm(df_p)

df$author_age <- year(df$month) * 12 + month(df$month) - 12 * year(df$author_first_commit) - month(df$author_first_commit)

      

df$share_commits <- df$n_commits / df$total_commits

rm(df_temp,df_t)

df$author_life <- year(df$author_last_commit) * 12 + month(df$author_last_commit) - 12 * year(df$author_first_commit) - month(df$author_first_commit)

summary(df)

```

First of all, we need to create a measure of users age within the GitHub platform. We set a user to have age 0 to the month in which the user makes the first commit. The question here is the following: how do users behave over their life on Github? Do they contribute greatly to a project, and then stop contributing? Or do they contribute to multiple projects over their lite time? In other words, are users very intensive in the contribution, or do they smooth it out during their life-time. 

In order to answer these questions, I compute for each users, the share of commits that that user has made in his/her most productive month over the total number of commits that person has made in her life-time on Github. From the histogram below, we see that a significant number of users contribute to at least 95% of the total number of commits they make in a month. As expected, there is a negative correlation between the share of the maximum number of commits in a month (measure of intensity of contribution) and the total number of commits made (measure of overall productivity). In order to avoid capturing users who are in early stages of their life-cycle on GitHub, we make eliminate users who have enter Github (by committing) later than January 2018.

The results presented below suggest that there is a significant presence of users who contribute intensively, in the sense that the month in which they committed the most corresponds to most of the activity they perform over their entire life on Github. 

```{r,echo=FALSE}
filter_productivity_commits_min <- 1
filter_productivity_commits_max <- 250000

df_temp <- df %>%
           group_by(author_id) %>%
           summarize(max_share=max(share_commits),total_commits=max(total_commits)) %>%
           filter(total_commits>=filter_productivity_commits_min,total_commits<filter_productivity_commits_max)

hist(df_temp$max_share,
     main='Commits in the most Productive Month, 
     as a Share of Total number of Commits made',
     xlab='Share',
     ylab='N. Users')

plot(log(df_temp$total_commits),log(df_temp$max_share),
     main='Log-share of Commits in Most Productive month vs. 
     Log-Total Number of Commits',
     xlab='Log-Total Commits',
     ylab='Log-Share')

df_temp <- df %>%
           group_by(author_id) %>%
           filter(share_commits==max(share_commits)) %>%
           filter(author_age==min(author_age)) %>%
           filter(total_commits>=filter_productivity_commits_min,total_commits<filter_productivity_commits_max) %>%
           filter(author_first_commit>='2010-01-01')


hist(df_temp$author_age,
     main='Age of the User at Largest Contribution',
     ylab='N. Users',
     xlab='Age',
     breaks=0:120)



```
We consider here another measure of productivity, which correlates with the number of commits made in total by a user. Considering that ultimately we are measuring the activity of users by the decision to commit, now for each user, we count the total number of periods an user has been active, and we classify users accordingly. For each category of user, we then compute the average number of commits the users in the category have made in their lite on GitHub, the total number of commits made by a category. As we can see, 33% of users contributed in at most one month, contributing to approximately 2% of the total commits. Another 26% of the users contributed for a total of 2-3 months, and a total 5.7% of the total number of commits. These two together represent the most casual contributors to GitHub, and represent approximately 60% of users. It is probably important to remove the more casual users, since it would be hard to justify their contributions in light of the variation in the observables. 

```{r}
df_temp <- df %>%
           group_by(author_id) %>%
           filter(total_commits>=filter_productivity_commits_min,
                  total_commits<filter_productivity_commits_max,
                  author_first_commit>='2010-01-01') %>%
           filter(n_commits>0) %>%
           summarize(period_active=n(),
                     total_commits=sum(n_commits),
                     n_projects=max(n_projects),
                     n_languages=max(n_languages),
                     n_projects_monthly=mean(n_projects_monthly)) 

compute_table <- function(df_temp,lb,ub){
  
  result <- df_temp %>% 
              filter(period_active<=ub,period_active>=lb) %>%      
              summarise(average_total_commits=mean(total_commits),
                        n_obs=n(),
                        total_commits=sum(total_commits),
                        average_projects=mean(n_projects),
                        n_languages=mean(n_languages),
                        n_projects_monthly=mean(n_projects_monthly))

    result <- as.numeric(result)

  return(result)
  
}

store <- matrix(0,6,8)
store[1,1:6] <- compute_table(df_temp,0,1)
store[2,1:6] <- compute_table(df_temp,2,3)
store[3,1:6] <- compute_table(df_temp,4,6)
store[4,1:6] <- compute_table(df_temp,7,12)
store[5,1:6] <- compute_table(df_temp,13,36)
store[6,1:6] <- compute_table(df_temp,37,200)                        
store[,7] <- store[,3] / sum(store[,3])
store[,8] <- store[,2] / sum(store[,2])
colnames(store) <- c('Average Tot. Commits', 'N. Users','Total Number of Commits','Average N. Of Projects','Avg. Number of Languages','N. of Projects Per Month, if Active','Share of Total Commits','Share of Total Users')
rownames(store) <- c('1 month','2-3 months', '4-6 months', '7-12 months', '13-36 months', '36+ months')

print(round(store,3))
```

```{r}

compute <- function(df,lb,ub){
  

  n<- df %>% 
      filter(author_age>=0, n_projects_monthly>=2,n_active_months>=lb,n_active_months<=ub) %>%
      summarise(n())
  
  N <- df %>% 
      filter(author_age>=0, n_projects_monthly>=1,n_active_months>=lb,n_active_months<=ub) %>%
      summarise(n())
  
  M <- df %>% 
      filter(author_age>=0, n_projects_monthly>=0,n_active_months>=lb,n_active_months<=ub) %>%
      summarise(n())
  
  return(c(as.numeric(n/N),as.numeric(n/M)))

}

store <- matrix(0,6,2)

store[1, ]<- compute(df,1,1)
store[2, ]<- compute(df,2,3)
store[3, ]<- compute(df,4,6)
store[4, ]<- compute(df,7,12)
store[5, ]<- compute(df,13,36)
store[6, ]<- compute(df,37,120)

rownames(store) <- c('1 month','2-3 months', '4-6 months', '7-12 months', '13-36 months', '36+ months')
colnames(store) <- c('Share of Observations in which Users are Active','Share of Total Observations')


print(round(store,3))

```



```{r}

plot_life_profile <-function(lb,ub,title){
    df_temp <- df %>% 
               group_by(author_id) %>% 
               mutate(active=as.numeric(n_commits>0)) %>%
               filter(sum(active)>=lb,sum(active)<=ub)%>%
               filter(author_age<=author_life,author_age>=0) %>%
               group_by(author_age) %>%
               summarise(n=mean(n_commits),p=mean(active))   

    df_temp_1 <- df %>% 
               group_by(author_id) %>% 
               mutate(active=as.numeric(n_commits>0)) %>%
               filter(sum(active)>=lb,sum(active)<=ub)%>%
    #           filter(author_age<=author_life) %>%
               group_by(author_age,author_age>=0) %>%
               summarise(n=mean(n_commits),p=mean(active))  
    
    plot(df_temp$p[2:84],
         xlab='Age of the Users in Months',
         ylab='N. Commits',
         main=title,
         ylim=c(min(df_temp_1$p),max(df_temp$p)),
         type = "l",
         lty = 1,
         col = 'blue')

    lines(df_temp_1$p[2:84],col='red')
    legend("topright", legend = c("Removed Users who Exit", "Included Users who Exit"),
           col = c("blue", "red"), lty = c(1,1), cex = 0.8)
    
    return()

    
}

plot_life_profile(37,200,'Probability of Making at least one Commit vs. Age, Active 36+ months')
plot_life_profile(13,36,'Probability of Making at least one Commit vs. Age, Active 13-36 months')
plot_life_profile(7,12,'Probability of Making at least one Commit vs. Age, Active 7-12 months')
plot_life_profile(3,6,'Probability of Making at least one Commit vs. Age, Active 3-6 months')
```

```{r,echo=FALSE}
plot_projects_profile <-function(lb,ub,title){
    df_temp <- df %>% 
               group_by(author_id) %>% 
               mutate(active=as.numeric(n_commits>0)) %>%
               filter(sum(active)>=lb,sum(active)<=ub)%>%
               filter(author_age<=author_life,author_age>=0) %>%
               group_by(author_age) %>%
               summarise(n=mean(n_projects_monthly))   

    df_temp_1 <- df %>% 
               group_by(author_id) %>% 
               mutate(active=as.numeric(n_commits>0)) %>%
               filter(sum(active)>=lb,sum(active)<=ub,author_age>=0)%>%
      
    #           filter(author_age<=author_life) %>%
               group_by(author_age) %>%
               summarise(n=mean(n_projects_monthly))  
    
    plot(df_temp$n[2:84],
         xlab='Age of the Users in Months',
         ylab='N. Commits',
         main='',
         ylim=c(min(df_temp_1$n[2:84]),max(df_temp$n[1:84])),
         type = "l",
         lty = 1,
         col = 'blue')

    lines(df_temp_1$n[2:84],col='red')
    legend("topright", legend = c("Removed Users who Exit", "Included Users who Exit"),
           col = c("blue", "red"), lty = c(1,1), cex = 0.8)
    
    return()

}

plot_projects_profile(37,200,'Average N. of Projects vs. Age, Active 36+ months')

plot_projects_profile(13,36,'Average N. of Projects vs. Age, Active 13-36 months')

plot_projects_profile(7,12,'Average N. of Projects vs. Age, Active 7-12 months')

plot_projects_profile(4,6,'Average N. of Projects vs. Age, Active 4-6 months')
```





#Users Exit
```{r}
df$active <- df$n_commits>0
df$month_numeric <- year(df$month) * 12 + month(df$month)

df_temp <- df %>%
           filter(share_commits<1) %>%
           select(month_numeric,active,author_id)

df_t <- expand.grid(author_id = unique(df_temp$author_id),
                    month_numeric = unique(df_temp$month_numeric))

df_temp <- df_t %>% left_join(df_temp,by=c('author_id','month_numeric'))

N_authors <- as.numeric(df_temp %>% summarise(n_distinct(author_id)))
N_periods <- as.numeric(df_temp %>% summarise(n_distinct(month_numeric)))

list_users <- unique(df_temp$author_id)
list_periods <- unique(df_temp$month_numeric)

history_activity <- matrix(0,N_authors,N_periods)

df_temp <- df_temp[order(df_temp$author_id),]
df_temp$active[is.na(df_temp$active)] <- FALSE 

c_m <- 1
for (month in list_periods){
  
    df_ttemp <- df_temp[df_temp$month_numeric==month, ]
    active <- df_ttemp$active[order(df_ttemp$author_id)]
    
    
    if (length(active)>0){

      if (c_m>1){

              history_activity[,c_m] <- (history_activity[,c_m-1] + 1) * (1 - active)
                
      } else{
        
              history_activity[,c_m] <- 1 - active
        
      }

    }
    
    c_m <- c_m + 1

  }
  



```

```{r,echo=FALSE}
ha <- apply(history_activity, 1, function(row) all(row>0))
history_activity_r <- history_activity[!ha,]

store <- matrix(NA,nrow(history_activity_r),3)
store[,1] <- apply(history_activity_r,1, function(x) min(which(x==0)))
store[,2] <- apply(history_activity_r,1, function(x) max(which(x==0)))
store[,3] <- store[,2] - store[,1]

 hist(store[,3],
      main='',
      xlab='Max Number of Months of Inactivity followed by Subsequent Commit')
 
print(quantile(store[,3],c(0.80,0.90,0.95,0.99)))



           
```



